\newcommand{\contenido}{
	\newpage
%	\phantomsection
	\currentpdfbookmark{Content}{Content}
	\tableofcontents
	%\thispagestyle{empty}
    %\newpage\null\thispagestyle{empty}
}

\newcommand{\figuras}{
	\newpage
	\phantomsection
	\addcontentsline{toc}{chapter}{\bf LIST OF FIGURES}
	\listoffigures
	%\thispagestyle{empty}
}


\newcommand{\tablas}{
	%\newpage
	%\phantomsection
	%\addcontentsline{toc}{chapter}{\bf LIST OF TABLES}
	%\listoftables
	%\thispagestyle{empty}
}


\newcommand{\acronimos}{
	\newpage
	\phantomsection
	\addcontentsline{toc}{chapter}{\bf LIST OF ACRONYMS}
	\chapter*{LIST OF ACRONYMS}
	\markboth{}{LIST OF ACRONYMS}

    % Create database with list of acronyms
    \DTLnewdb{acronyms}
    \addacronym{NA}{Numerical aperture.}
    \addacronym{DoF}{Depth of field.}
    \addacronym{FoV}{Field of view.}
    \addacronym{ISAM}{Interferometric synthetic aperture microscopy.}
    \addacronym{CAC}{Computational aberration correction.}
    \addacronym{CAO}{Computational adaptive optics.}
    \addacronym{AO}{Adaptive optics.}
    \addacronym{PS-OCT}{Polarization-sensitive optical coherence tomography.}
    \addacronym{OCT-A}{Optical coherence tomography angiography.}
    \addacronym{SAR}{Synthetic aperture radar.}
    \addacronym{SNR}{Signal-to-noise ratio.}
    \addacronym{SHARP}{Short Aline-Range Phase-stability adaptive optics.}
    \addacronym{CTNode}{Coherent tomographic non-local means denoising.}
    \addacronym{TNode}{Tomographic non-local means despeckling.}
    \addacronym{PS-TNode}{Polarization-sensitive tomographic non-local means despeckling.}
    \addacronym{OPL}{Optical path length.}
	\addacronym{OCT}{Optical coherence tomography.}
	\addacronym{TDOCT}{Time-domain optical coherence tomography.}
	\addacronym{SDOCT}{Spectral-domain optical coherence tomography.}
	\addacronym{FDOCT}{Fourier-domain optical coherence tomography.}
	\addacronym{SSOCT}{Swept-source optical coherence tomography.}
	\addacronym{OFDI}{Optical frequency domain imaging.}
	\addacronym{FF}{Full-field.}
	\addacronym{LF}{Line-field.}
	\addacronym{OCM}{Optical coherence microscopy.}
	\addacronym{PSF}{Point spread function.}
	\addacronym{FT}{Fourier transform.}
	\addacronym{SOA}{Semiconductor optical amplifier.}
	\addacronym{FBG}{Fiber Bragg grating.}
	\addacronym{ADC}{Analog-to-digital conversions.}
	\addacronym{VCSEL}{Vertical cavity surface emitting lasers.}
	\addacronym{MEMS}{Micro-electro-mechanical mirror system.}
	\addacronym{2D}{Two dimensional.}
	\addacronym{1D}{One dimensional.}
	\addacronym{3D}{Three dimensional.}
	\addacronym{MS}{Multiple scattering.}
	\addacronym{STD}{Standard deviation.}
    \addacronym{BFL}{Back focal length.}
    \addacronym{FFL}{Front focal length.}
    \addacronym{FM}{Forward model.}
    \addacronym{SE}{Shannon's Entropy.}
    \addacronym{MPS}{Mean power spectrum.}
    \addacronym{RB}{Rollback.}
    \addacronym{OF}{Optimum filter.}
    \addacronym{OoF}{Out of focus.}
    \addacronym{ROI}{Region of interest.}
    \addacronym{DOP}{Degree of polarization.}
    \addacronym{SLO}{Scanning laser ophthalmoscope.}

    \DTLsort{Acronym}{acronyms}
    % Display the contents of the database
    \begin{itemize}
    \DTLforeach*{acronyms}{\thisAcronym=Acronym,\thisDesc=Description}%
       {\item[] \textbf{\thisAcronym},\tabto{5.7em} \quad\thisDesc}%
    \end{itemize}

	%\thispagestyle{empty}
}

\contenido
\figuras
%\tablas
\acronimos
\newpage\null\thispagestyle{empty}
